\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{mathtools}

\newcommand{\R}{\mathcal{R}}
\newcommand{\Rcv}{\mathsf{R}}
\newcommand{\Snd}{\mathsf{S}}
\newcommand{\IS}{\mathsf{IS}}
\newcommand{\Enc}{\mathsf{Enc}}
\newcommand{\Dec}{\mathsf{Dec}}
\newcommand{\PlainMult}{\mathsf{PlainMult}}
\newcommand{\PlainAdd}{\mathsf{PlainAdd}}
\newcommand{\CtxtAdd}{\mathsf{CtxtAdd}}
\newcommand{\OPRF}{\mathsf{OPRF}}
\newcommand{\Zp}{\mathbb{Z}_p}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\sigmin}{\sigma_{\min}}
\DeclareMathOperator{\row}{row}
\newcommand{\half}{\tfrac{1}{2}}

\title{\textbf{Private Encrypted Data Alignment by ID}\\[4pt]
\large A design note: extending OKVS/RLWE Reverse-PMT to payload transport}
\author{Working notes}
\date{\today}

\theoremstyle{definition}
\newtheorem{remark}{Remark}
\newtheorem{problem}{Open problem}

\begin{document}
\maketitle

\begin{abstract}
We sketch how to repurpose the OKVS-based, RLWE-instantiated Reverse-PMT (RPMT) of the
companion paper into a \emph{private encrypted data alignment} primitive: a receiver
$\Rcv$ holds a table $\{(\mathsf{ID}_i,\mathsf{payload}_i)\}$ and a sender $\Snd$ holds a
set of IDs; for each of $\Snd$'s IDs that matches one of $\Rcv$'s, $\Snd$ obtains an
\emph{encryption} of the corresponding payload, aligned to $\Snd$'s own order, so that
$\Snd$ can run a homomorphic analysis on the aligned payloads together with its own data.
The two non-trivial pieces are (i) neutralizing the OKVS ``garbage'' on non-matching IDs
without leaking the join pattern, via a secret-shared membership indicator and a single
ciphertext$\times$ciphertext mask, and (ii) carrying real-valued payloads in CKKS, which
turns the OKVS encoding problem from a finite-field full-rank question into a
\emph{numerical conditioning} question. We record the design decisions and the resulting
research questions.
\end{abstract}

\section{Setting and target functionality}

Let $\Rcv$ (receiver, data owner) hold a key--value table
$T=\{(\mathsf{ID}_i,\mathsf{payload}_i)\}_{i\in[n_x]}$ and let $\Snd$ (sender) hold a set of
identifiers $\{\mathsf{ID}^\Snd_j\}_{j\in[n_y]}$. We want a protocol that delivers to $\Snd$,
for each $j$, an \emph{encryption} of $\mathsf{payload}_i$ whenever
$\mathsf{ID}^\Snd_j=\mathsf{ID}_i$ for some $i$, and an encryption of (effectively) zero
otherwise; the result is aligned to $\Snd$'s own indexing. $\Snd$ then evaluates an
application-specific homomorphic function on these aligned ciphertexts and its own
plaintext data. Throughout, $\Rcv$ holds the RLWE secret key(s); all ciphertexts handed to
$\Snd$ are under $\Rcv$'s public key, so $\Snd$ computes but cannot decrypt. The final
analysis output is returned to $\Rcv$ (or kept secret-shared); this delivery and the choice
of analysis are treated as out of scope here.

\section{Recap of the base RPMT mechanism}

The base construction (companion paper) realizes
$F_{\mathrm{RPMT}}$: $b_j=\mathbf{1}(y_j\in X)$. Its mechanics that we reuse:
\begin{enumerate}[leftmargin=*]
  \item $\Rcv$ OKVS-encodes $\{(x_i',\IS)\}$ --- \emph{same} indicator value $\IS$ for
  every key --- into $p$, using the \emph{Random Spaced Band} (RSB) matrix (a fixed column
  permutation $\pi_N$ of a random-band matrix, aligning bands to the RLWE slot size $N$).
  \item $\Rcv$ RLWE-encrypts $p$ (block-packed, plus pre-rotated copies) and sends it.
  \item $\Snd$ homomorphically evaluates the OKVS decoding $M\cdot p$ as a
  (block-)diagonal matrix--vector product, using only slot-wise $\PlainMult/\CtxtAdd$.
  \emph{Sequencing} (Algorithm~3 of the paper) splits the collision-laden matrix into $L$
  layers $\bar M_t\in\Zp^{N\times m}$, each with $\le w+\zeta$ diagonals; the assignment of
  item $i$ to layer/slot $(\mu_i,\tau_i)$ depends only on the band start
  $a_i=H_1(k_i)$, the slot count $N$, and the span limit $\zeta$ --- \emph{not} on $w$.
  \item Each decoded slot is $\IS$ if $y_j\in X$ and a pseudorandom value otherwise. The
  base protocol re-randomizes, returns the $L$ ciphertexts to $\Rcv$, who tests equality
  with $\IS$.
\end{enumerate}
A key efficiency point: sequencing is an $n$-balls-into-$N$-bins process, so its batching
efficiency relies on the regime $N\ll n$ (well-filled slots). The base parameters fix
$N=2^{13}$ for all $n\in[2^{16},2^{22}]$.

\paragraph{Secret-shared PMT (Appendix~D).} Masking the decoded plaintext by $r_\mu$ before
$\Rcv$ decrypts, followed by a secret-shared equality test $F_{\mathrm{ss\text{-}peqt}}$,
yields XOR shares $b_{X,i}$ (held by $\Rcv$) and $b_{Y,i}$ (held by $\Snd$) with
$b_{X,i}\oplus b_{Y,i}=\mathbf 1(y_i\in X)$. We reuse this verbatim for the indicator.

\section{The alignment construction}

\subsection{From indicator to payload: two OKVS instances}

Replace the single all-$\IS$ OKVS by \emph{two} OKVS instances sharing the same keys
$k_i=\OPRF(\mathsf{ID}_i)$:
\begin{itemize}[leftmargin=*]
  \item an \emph{indicator} OKVS over a finite field (values all $=\IS$, or all $=1$), used
  exactly as in the base protocol to produce the membership shares $b_{X,i},b_{Y,i}$;
  \item a \emph{payload} OKVS whose value for key $k_i$ is $\mathsf{payload}_i$, decoded
  homomorphically so that $\Snd$ holds an RLWE ciphertext whose slot for $y_j$ contains
  $\mathsf{payload}_i$ (match) or pseudorandom garbage (non-match).
\end{itemize}
With a generic payload, the decoded value alone no longer certifies membership (garbage is
indistinguishable from a real payload), which is exactly why the separate indicator is
needed.

\subsection{Removing the garbage without leaking the join}

After the indicator ssPMT, $\Snd$ holds the garbage-laden payload ciphertext, its own share
$b_{Y,i}$, and knows the slot of each $y_j$; $\Rcv$ holds $b_{X,i}$. Let $b_i=b_{X,i}\oplus
b_{Y,i}$ be the (secret) membership bit. To zero out non-matches while keeping $b_i$ hidden
from both parties:
\begin{enumerate}[leftmargin=*]
  \item $\Rcv$ encrypts its share $b_{X,i}$ (packed into the payload slot layout) and sends
  $\Enc(b_{X,i})$ to $\Snd$.
  \item $\Snd$ forms $\Enc(b_i)$ \emph{using only plaintext operations}, because its own
  share $s:=b_{Y,i}$ is a known constant per slot:
  \begin{equation}\label{eq:xor}
    b_i = b_{X,i}\oplus s = (1-2s)\,b_{X,i} + s
    \;\;\Longrightarrow\;\;
    \Enc(b_i)=\PlainAdd\!\big(\PlainMult(\Enc(b_{X,i}),\,1-2s),\ s\big).
  \end{equation}
  (Note $a\oplus b=a+b-2ab$, not $a+b-ab$; the latter is OR.) No
  ciphertext$\times$ciphertext product is needed here.
  \item $\Snd$ multiplies the membership ciphertext by the payload ciphertext:
  \[
    \Enc(\widetilde{\mathsf{payload}})
    = \Enc(b_i)\odot \Enc(\mathsf{payload}\text{-or-garbage}).
  \]
  This is the \emph{single} ciphertext$\times$ciphertext multiplication of the construction:
  on a match it returns $\mathsf{payload}$, on a non-match $0\cdot\text{garbage}$.
\end{enumerate}
The membership bit never appears in the clear to either party, so the join pattern is
hidden from $\Snd$. The masking multiplication takes the protocol out of the base paper's
``additive-only'' regime by exactly one multiplicative level (plus relinearization),
which must be accounted for in the modulus budget.

\begin{remark}[circuit privacy]
Since $\Snd$'s computation touches the ciphertext before $\Rcv$ decrypts the final analysis
output, noise-flooding / circuit privacy must be applied before that decryption, exactly as
the base protocol does on its returned ciphertexts.
\end{remark}

\subsection{Scheme split: indicator in BGV/BFV, payload in CKKS}
Real-world payloads are typically real numbers, so the payload OKVS is naturally carried in
CKKS while the indicator/equality logic stays in BGV/BFV. The re-encryption of $b_{X,i}$ into
CKKS is free: the share is plaintext to its holder, so no scheme-switching
primitive is required --- $\Rcv$ simply CKKS-encrypts a fresh $0/1$, and \eqref{eq:xor} runs
in CKKS. The only semantic change from the BGV masking is that \emph{exact} zeroing becomes
\emph{approximate}: with $b_i=0\pm\delta$, a non-match leaves a residual $\delta\cdot
\text{garbage}$. Hence the central numerical requirement:
\[
  \norm{p}\le \frac{\norm{v}}{\sigmin(M)},\qquad
  |\text{garbage}|=|\langle\row(y'),p\rangle|\le \sqrt{w}\,\norm{p},\qquad
  \text{CKKS residual}\sim \delta\cdot|\text{garbage}|,
\]
so controlling $\sigmin(M)$ (equivalently $\norm{p}$) is what keeps the residual below the
analysis tolerance (Section~\ref{sec:real}).

\subsection{Slot geometry and the ``promote later'' parameter plan}
BGV/BFV with ring dimension $N$ has $N$ slots; CKKS with ring dimension $N'$ has $N'/2$
slots. To share one sequencing grid between the two decodes (so $\Rcv$ packs its membership
share once, with no cross-grid permutation), the slot counts must match. The clean way is to
choose the CKKS ring as $N'=2N$, which CKKS likely needs anyway for the masking depth and
payload precision. Then both have $N$ slots and the $(\mu_i,\tau_i)$ layout is identical
(it depends only on $H_1$, the slot count, and $\zeta$; $w$ and the band values may differ
between the two instances).

Two further points drive the parameterization:
\begin{itemize}[leftmargin=*]
  \item \textbf{Keep $N$ small during alignment.} Sequencing is $n$-balls-into-(slot count);
  large slot counts under-fill the bins and waste computation on near-empty ciphertexts. The
  alignment phase should run at modest $N$ (e.g.\ BFV $2^{13}$ / CKKS $2^{14}$), preserving
  $N\ll n$.
  \item \textbf{Bootstrap is not a dimension lift.} $N$ is fixed at key generation;
  bootstrapping refreshes the modulus/level at the \emph{same} $N$. If deep analysis is
  needed, one keeps alignment at small $N$ and, \emph{after} masking (alignment done),
  ring-switches the aligned payload \emph{up} to a large ring and bootstraps there
  (a sparse-slot, hence favorable, bootstrapping). The big-$N$ bootstrapping keys must be
  provisioned upfront, but the shallow alignment work stays cheap at small $N$. Ring
  switching \emph{down} (large$\to$small) is the genuinely useful direction for shrinking
  the tail; ring switching \emph{up} grants no fresh noise budget by itself --- only the
  subsequent bootstrap does.
\end{itemize}

\section{Real-field OKVS: conditioning instead of rank}\label{sec:real}

For the payload OKVS over $\mathbb{R}$ (CKKS) we use \emph{Gaussian} random bands: each
width-$w$ band has i.i.d.\ $\mathcal N(0,1)$ coefficients, placed at a random start. The
encoding solves $M p=v$ over $\mathbb{R}$, where $M$ is $n\times m$,
$m\approx(1+\varepsilon)n$.

\paragraph{Why Gaussian, not binary.}
The earlier motivation for $0/1$ bands was an ``addition-only'' homomorphic decode, but this
is illusory: the decode is $\sum_k \mathsf{PlainMult}(\rho_k(c),\,\mathrm{diag}_k)$, and a
$\mathsf{PlainMult}$ costs the same whether the plaintext diagonal is $0/1$ or real (it is
encoded into a dense plaintext polynomial and NTT-multiplied regardless); binary also gives
no encoding-time speedup off $\mathrm{GF}(2)$. Meanwhile full-entropy real coefficients
condition markedly better --- experimentally $\sigmin$ is $\sim\!1.7\times$ larger at equal
$w$, so Gaussian bands reach a target $\sigmin$ with $\sim\!1/3$ fewer diagonals --- and
admit clean random-matrix tools (continuous anti-concentration) for the analysis below.

\paragraph{Rank is automatic; conditioning is the whole question.}
For Gaussian bands full row rank holds almost surely (the only structural requirement is that
the sparsity pattern admits a row-to-column matching, which holds once $(\varepsilon,w)$
clear the RB-OKVS thresholds). So unlike the finite-field case there is no rank-failure event
to bound; CKKS instead needs $\sigmin(M)$ bounded \emph{away from $0$}, since a full-rank $M$
with tiny $\sigmin$ already yields an exploding $\norm{p}$. The operative target is a
\emph{smallest-singular-value tail bound}
\[
  \Pr[\sigmin(M)<t]\le 2^{-\lambda},
\]
which replaces the finite-field rank-failure bound and which sets $(\varepsilon,w)$; a proof
sketch is given in Section~\ref{sec:sigmin}. Redundancy $\varepsilon$ (extra columns) is the
primary knob --- it sets the spectral gap $\sigmin\gtrsim\sqrt m-\sqrt n$ --- with $w$
secondary, as the experiments confirm.

\paragraph{Efficient minimum-norm encoding.}
Among all valid encodings $\{p_0+\ker M\}$ the minimum-$\ell_2$-norm solution is
$p^\star=M^\top(MM^\top)^{-1}v$, and its size is governed precisely by $\sigmin$:
$\norm{p^\star}\le\norm{v}/\sigmin(M)$. Crucially this is cheap to compute for band
matrices: ordering rows by band start makes $MM^\top$ \emph{banded} (bandwidth $O(w)$), so
$MM^\top y=v$ is solved by banded Cholesky in $O(nw^2)$ and $p^\star=M^\top y$ in $O(nw)$ ---
comparable to the encoding itself, and far smaller in norm than the naive triangular
particular solution (free variables set to $0$), whose norm is governed by the worse-
conditioned pivot submatrix. (Normal equations square the condition number; a banded QR of
$M^\top$ is the stable fallback.)

\section{A proof sketch for the $\sigmin$ tail bound}\label{sec:sigmin}

We sketch the route to $\Pr[\sigmin(M)<t]\le 2^{-\lambda}$; constants and the precise
threshold $t=t(\varepsilon,w)$ are deferred, and the empirical $(\varepsilon,w)\mapsto\sigmin$
surface of the accompanying experiment is what they must fit. The model: $M\in\mathbb
R^{n\times m}$, $m=(1+\varepsilon)n$; row $i$ is supported on the window $[a_i,a_i+w)$ with
$a_i\sim U[0,m-w]$ i.i.d., and the $w$ in-band entries are i.i.d.\ $\mathcal N(0,1)$. Write
$r_1,\dots,r_n$ for the rows. Since $n\le m$,
\[
  \sigmin(M)=\min_{u\in S^{n-1}}\norm{M^\top u}_2,\qquad
  M^\top u=\sum_{i=1}^n u_i\,r_i\ \in\mathbb R^m,
\]
and we must show this minimum is $\gtrsim t$ with high probability. We use the
small-ball / $\varepsilon$-net method of Rudelson--Vershynin and Litvak--Pajor--Rudelson--
Tomczak-Jaegermann, where the band structure enters through \emph{column independence}.

\paragraph{Step 1 (column independence --- the structural heart).}
Condition on the starts $\{a_i\}$. The $j$-th coordinate of $M^\top u$ is
$(M^\top u)_j=\sum_{i:\,j\in[a_i,a_i+w)} u_i\,M_{ij}$. Distinct columns use disjoint sets of
the i.i.d.\ Gaussian entries, so the coordinates $\{(M^\top u)_j\}_{j\in[m]}$ are
\emph{independent}, with
\[
  (M^\top u)_j\sim\mathcal N\!\big(0,\,s_j^2(u)\big),\qquad
  s_j^2(u)=\!\!\sum_{i:\,j\in[a_i,a_i+w)}\!\!u_i^2,\qquad
  \sum_{j=1}^m s_j^2(u)=\sum_i u_i^2\,w=w .
\]
Thus $\norm{M^\top u}^2=\sum_j s_j^2(u)\,Z_j^2$ is a sum of \emph{independent} terms with mean
$w$. Band sparsity is exactly what makes the image coordinates independent --- this is what a
dense-matrix argument gets for free and a general sparse matrix does not.

\paragraph{Step 2 (single-direction small ball, by tensorization).}
For a fixed $u$, the independence of the coordinates lets us tensorize the per-coordinate
Gaussian anti-concentration $\Pr[|(M^\top u)_j|\le\rho\,s_j(u)]\le C\rho$: by the
Rudelson--Vershynin tensorization lemma,
\[
  \Pr\!\big[\norm{M^\top u}\le \rho\,\sqrt{\textstyle\sum_j s_j^2(u)}\big]
  \;\le\;(C\rho)^{\,\kappa(u)},
\]
where $\kappa(u)=\#\{j:s_j^2(u)>0\}$ is the number of \emph{active columns} --- the size of
the union of the bands of the rows on which $u$ is supported. The exponent is therefore the
column-spread of the direction; this is the quantity the redundancy $\varepsilon$ and width
$w$ control.

\paragraph{Step 3 (incompressible / compressible split).}
Decompose $S^{n-1}$ into spread and sparse directions (Rudelson--Vershynin):
\begin{itemize}[leftmargin=*,topsep=2pt]
  \item \emph{Incompressible $u$:} a constant fraction of the mass sits on $\Theta(n)$
  coordinates, so the active bands cover $\kappa(u)=\Theta(m)=\Theta((1+\varepsilon)n)$
  columns; Step 2 gives a single-direction bound $(C\rho)^{\Theta(n)}=e^{-\Theta(n)}$, which
  beats the $e^{O(n)}$ cardinality of an $\varepsilon$-net of the sphere (for $\varepsilon$
  bounded below). With $\norm{M^\top\cdot}$ being $\sigma_{\max}(M)$-Lipschitz and
  $\sigma_{\max}=O(\sqrt w+\sqrt{m})$ w.h.p., a union bound controls all incompressible
  directions and yields $\norm{M^\top u}\gtrsim \sqrt m-\sqrt n$ there.
  \item \emph{Compressible $u$ ($\approx k$-sparse):} the $k$-sparse net has only
  $e^{O(k\log(m/k))}$ points, while a $k$-sparse direction still activates
  $\kappa(u)=\Omega(w)$ columns (its bands are nearly disjoint for random starts), giving a
  per-point small ball $e^{-\Omega(w)}$. Balancing $k\log(m/k)$ against $w$ closes the union
  bound once $w=\Omega(\log n)$, with failure $e^{-\Omega(w)}$.
\end{itemize}

\paragraph{Step 4 (the random sparsity pattern is good).}
Steps~1--3 condition on $\{a_i\}$ and need the pattern ``well spread'': every column is
covered by $O\!\big(w/(1+\varepsilon)\big)$ bands and every union of $k$ bands covers
$\Omega(\min(kw,m))$ columns. As $a_i\sim U[0,m-w]$ i.i.d., these are balls-into-bins
statements holding except with probability $e^{-\Omega(w)}$ (Chernoff), absorbed into the
budget.

\paragraph{Conclusion.}
Combining, there are constants $c,c'$ and a threshold $t_0=t_0(\varepsilon)$ of order
$\sqrt m-\sqrt n=\sqrt n\,(\sqrt{1+\varepsilon}-1)$ such that
\[
  \Pr\big[\,\sigmin(M)< c\,t_0\,\big]\;\le\;e^{-c'\min(n,\,w)} .
\]
The two parameters play distinct roles: $\varepsilon$ fixes the conditioning \emph{scale}
$t_0$ (the spectral gap) and powers the incompressible exponent, while $w$ powers the
compressible exponent and the good-pattern event. Taking $\varepsilon$ a constant bounded
below and $w=\Omega(\lambda)$ gives $\Pr[\sigmin<c\,t_0]\le 2^{-\lambda}$. This matches the
experiment, where $\sigmin$ rises with both $w$ and $\varepsilon$ and collapses to $\approx0$
as $\varepsilon\to0$ (the near-square regime), and where Gaussian coefficients --- whose
anti-concentration in Step~2 is the clean Gaussian small ball --- outperform binary ones
(which would instead need a Carbery--Wright / Berry--Esseen anti-concentration input).

\section{Open problems / next steps}

\begin{problem}[$\sigmin$ tail bound --- make the sketch rigorous]
Turn Section~\ref{sec:sigmin} into a theorem: pin the constants $c,c'$ and threshold
$t_0(\varepsilon)$ in $\Pr[\sigmin(M)<c\,t_0]\le e^{-c'\min(n,w)}$ for random width-$w$
\emph{Gaussian} band matrices with $m=(1+\varepsilon)n$, giving an explicit
$(\varepsilon,w)\mapsto t$ trade-off matching the measured surface. The compressible-net
balancing (Step~3) and the good-pattern event (Step~4) are the parts needing care.
\end{problem}

\begin{problem}[empirical conditioning]
Measure, for Gaussian band matrices over $\mathbb{R}$: the amplification
$\norm{p}/\norm{v}$ for naive-triangular vs.\ banded-min-norm; $\sigmin(M)$ and its
dependence on $(w,\varepsilon)$; and the resulting garbage magnitude
$|\langle\row(y'),p\rangle|$ on non-matches. (Addressed by the accompanying experiment, which
also confirms Gaussian bands beat binary at equal $w$.)
\end{problem}

\begin{problem}[2-row decode]
The $2\times(N/2)$ BGV hypercube admits, with $N/2$-based sequencing and rotation-during-
compute, two layer products per row-wise rotation --- halving plain-mults for the indicator
decode and resolving the open remark of \S4.3 of the base paper. The packing (offset
alignment of paired layers; replication vs.\ windowed layout) and its
communication/computation trade-off remain to be fixed.
\end{problem}

\end{document}
