% ===========================================================================
% KKLS follow-up note. Two topics (see docs/kkls-followup-brief.md):
%   (A) the dense two-row BGV decode using the full 2x(N/2) slot hypercube,
%   (B) the leakage of disclosing the receiver's decode layout in ssPMT.
%
% Provenance of the recovered material (both sources live in the companion
% yonghaason/Real-PJC repository, not in this one):
%   - Section 3 prose and Algorithm 2 are adapted from Real-PJC's
%     docs/encrypted-alignment-design.tex ("Pre-rotation vs. homomorphic
%     rotation", "The BGV dense two-row decode", "Output-swap refinement",
%     Open problem "2-row decode --- resolved").
%   - The recovered paper text (former realpjc.tex Sec. 3.1 "Variant with
%     Receiver-side Rotation" + "Optimality of the rotation count" + the
%     "Redundancy Sweep" appendix) was deleted by Real-PJC commit 043677f
%     ("Demote the HE decode section to Preliminaries; defer 2x(N/2)
%     material"); recovered via `git show 043677f^:docs/realpjc.tex` in that
%     repository. (The handoff brief cites the stale hash 2d828a1 for it.)
%
% Scope boundary: sigma_min tail bounds, real-field OKVS, and min-norm
% encoding belong to the Real-PJC paper, NOT to this note. The layout-leakage
% discussion overlaps with Real-PJC's "layout matching" argument; keep the
% conclusions consistent (there the OPRF direction prevents the sender from
% predicting coordinates; here, in standalone KKLS ssPMT, the sender knows
% F(x) and can predict them --- which is exactly what this note analyzes).
% ===========================================================================
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noEnd=true]{algpseudocodex}
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}
\newcommand{\LineComment}[1]{\State \rule{0pt}{3ex}\textit{//~#1}}
\newcommand{\sample}{\stackrel{\$}{\gets}}
\usepackage{xcolor}

% ---------------------------------------------------------------------------
%  Drafting: \TODO{...} renders as a red [TODO: ...].
% ---------------------------------------------------------------------------
\newcommand{\TODO}[1]{\textcolor{red}{[TODO: #1]}}
\newcommand{\VERIFY}[1]{\textcolor{orange}{[VERIFY: #1]}}

% ---------------------------------------------------------------------------
%  Functionality box (as in realpjc.tex)
% ---------------------------------------------------------------------------
\newsavebox{\funcboxsave}
\newenvironment{funcbox}
  {\begin{lrbox}{\funcboxsave}\begin{minipage}{0.93\linewidth}\smallskip}
  {\smallskip\end{minipage}\end{lrbox}\begin{center}\fbox{\usebox{\funcboxsave}}\end{center}}

% ---------------------------------------------------------------------------
%  Frequently-used macros (shared with realpjc.tex)
% ---------------------------------------------------------------------------
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Zp}{\mathbb{Z}_p}
\newcommand{\Enc}{\mathsf{Enc}}
\newcommand{\Dec}{\mathsf{Dec}}
\newcommand{\PMult}{\mathsf{PMult}}          % plaintext multiply (ctxt x plaintext)
\newcommand{\CAdd}{\mathsf{Add}}             % ciphertext add
\newcommand{\rr}{\rho}                       % row-rotation by r
\newcommand{\colswap}{\sigma}                % BGV column swap (swaps the two rows)
\newcommand{\Okvs}{\mathsf{OKVS}}
\newcommand{\HomDec}{\mathsf{HomDecode}}
\newcommand{\Snd}{\mathsf{S}}                % sender
\newcommand{\Rcv}{\mathsf{R}}                % receiver
\newcommand{\row}{\mathsf{row}}
\newcommand{\band}{w}                        % band width
\newcommand{\eps}{\varepsilon}               % OKVS expansion (m = (1+eps) n)
\newcommand{\half}{H}                        % H = N/2, slots per block / row length
\newcommand{\Fsspmt}{\mathcal{F}_{\mathsf{ssPMT}}}
\providecommand{\norm}[1]{\lVert #1 \rVert}
% Topic B macros
\newcommand{\Poi}{\mathrm{Poi}}
\newcommand{\Bin}{\mathrm{Bin}}
\newcommand{\TV}{\mathrm{TV}}
\newcommand{\LR}{\mathsf{LR}}
\newcommand{\occ}{\mathsf{occ}}
%
\begin{document}
%
\title{Notes on Batch Homomorphic OKVS Decoding:\\ the Dense Two-Row BGV Layout, and\\ the Cost of Layout Disclosure in ssPMT}
%\titlerunning{Dense two-row decoding and layout disclosure}
\author{\TODO{author list (follow-up to~\cite{EPRINT:KwaKwoLeeSon26})}}
\institute{\TODO{institutes}}
%
\maketitle
%
\begin{abstract}
\TODO{150--250 words. Two self-contained additions to the batch homomorphic OKVS
decoding framework of KKLS~\cite{EPRINT:KwaKwoLeeSon26}. (i)~A \emph{dense two-row}
BGV decode that uses the full $2\times(N/2)$ slot hypercube: two OKVS blocks per input
ciphertext, two sequenced query layers per output ciphertext, and a column-swap routing
that needs no per-output merge. With the output-swap rotation schedule the receiver
performs only $L/2+(\band{-}1)/2$ rotations under two Galois keys, and communication
becomes monotone in the OKVS expansion $\eps$ --- unlocking the small-$\eps$ regime
($-38\%$ communication at $\eps=0.2$ vs.\ the pre-rotated layout's U-shaped optimum).
(ii)~A leakage analysis of a natural ssPMT optimization: disclosing the receiver's
occupied decode positions to compress the secret-shared equality phase from $L\half$ to
$n_y$ instances. We show the disclosure is \emph{not} innocuous: the sender can predict
each candidate's slot column, the column multiplicity is a likelihood-ratio test with
per-candidate advantage $\approx1/\sqrt{2\pi\lambda}$ at fill rate $\lambda=n_y/\half$,
and --- qualitatively worse --- an empty column is a \emph{certain non-membership
certificate}, so sparse layouts leak catastrophically. Publishing the layout jointly
with a second predictable coordinate system (e.g.\ a cuckoo-bin correspondence) upgrades
the attack to an essentially perfect per-item membership test. We give the repairs:
evaluate over the full deterministic layout (constant-factor cost $1/\text{fill-rate}$,
trivial simulation), or state the leakage function explicitly and forbid sparse
parameters.}

\keywords{Oblivious key-value stores \and Homomorphic encryption \and Private
membership test \and Leakage analysis.}
\end{abstract}
%
% ===========================================================================
\section{Introduction}
\label{sec:intro}

\TODO{Frame as a follow-up note to KKLS~\cite{EPRINT:KwaKwoLeeSon26}: the base RPMT
paper introduced batch homomorphic OKVS decoding (spaced bands, sequencing) and the
ssPMT of its Appendix~D. This note settles two questions the base paper left on the
table: (A)~can the BGV decode use the \emph{full} $2\times(N/2)$ slot space without
per-output merges or replicated inputs, and at what rotation cost; (B)~is the
``publish the receiver's decode layout'' optimization of the standalone ssPMT safe.}

\subsection{Our Contribution}
\label{sec:intro:contrib}

\TODO{Contribution list, current plan:
\begin{enumerate}
  \item The dense two-row BGV decode (Section~\ref{sec:dense}): construction,
  correctness (row-wise, no merge), and the rotation-schedule space with an
  optimality discussion --- input-swap $m/N+(\band{-}1)$ vs.\ output-swap
  $L/2+(\band{-}1)/2$, and why replicated-$p$ and per-output-merge layouts are
  dominated.
  \item Integrated sequencing (Section~\ref{sec:dense:intseq}): fill both rows of a
  paired layer under one shared block window, projected $\PMult$ count
  $0.97$--$1.04\times$ the $N$-slot decode (vs.\ $1.18$--$1.41\times$ for the current
  sequence-then-pair implementation). Design, implementation, re-measurement.
  \item The layout-disclosure leakage analysis (Section~\ref{sec:leak}): leakage
  function, likelihood-ratio optimality (Neyman--Pearson), the
  $\TV=$ mode-mass identity with $\lambda$-scaling, the empty-column certificate, and
  the consistency-oracle amplification.
  \item Repairs with proofs (Section~\ref{sec:leak:repair}): full-layout /
  dummy-fill evaluation with a trivial simulator, or leakage-explicit compression
  with a $\lambda$ lower bound.
  \item Benchmarks: the recovered redundancy sweep (Appendix~\ref{app:epssweep}),
  extended by integrated sequencing and the ss-equality cost gap ($n_y$ vs.\
  $L\half$ instances).
\end{enumerate}}

\subsection{Related Work}
\label{sec:intro:related}
\TODO{KKLS~\cite{EPRINT:KwaKwoLeeSon26}; circuit-PSI ssPMT
instantiations~\cite{EC:PSTY19,AC:LPRST21}; BGV/BFV slot hypercube and rotation
machinery (Gentry--Halevi--Smart / HElib literature); membership-inference-style
leakage analyses in PSI-adjacent protocols. The companion Real-PJC paper uses the
same decode engine for CKKS alignment; its ``layout matching'' step is safe for a
different reason (the sender cannot evaluate the OPRF), which this note's analysis
makes precise.}

% ===========================================================================
\section{Background: the KKLS Decode and ssPMT}
\label{sec:prelim}

\subsection{Notation}
\label{sec:prelim:notation}
\TODO{Standard notation ($\kappa$, $\lambda_s$ statistical parameter, $[n]$, vectors,
etc.). BGV with ring dimension $N$: $N$ plaintext slots forming the hypercube
$\Z_{\half}\times\Z_2$ with $\half=N/2$ (Section~\ref{sec:dense:geometry});
$\rr_r$ is the $r$-slot row rotation (both rows rotate in parallel), $\colswap$
the column swap (the two rows exchange). OKVS with $n$ rows, $m=(1+\eps)n$
columns, band width $\band$.}

\subsection{Batch Homomorphic OKVS Decoding}
\label{sec:prelim:homdec}

We recall the batch decode of KKLS~\cite{EPRINT:KwaKwoLeeSon26}; this summary is what
Sections~\ref{sec:dense} and~\ref{sec:leak} build on.

\paragraph{Spacing the band.}
KKLS fix a \emph{spacing} column permutation $\pi_\half$ on top of the random-band OKVS:
regroup the $m$ coordinates into $b=m/\half$ blocks of $\half$, and place the $\band$
in-band coordinates of each row into $\band$ \emph{consecutive blocks, one coordinate
per block, at a common intra-block slot}. We call this variant the random
\emph{spaced}-band (RSB) OKVS. The permutation is fixed and public, so encoding is
unchanged up to reindexing; its purpose is purely to align the decode with the slot
structure of batched HE.

\paragraph{The decode.}
The batch decode evaluates many OKVS decodings \emph{under encryption}: one party holds
ciphertexts of the OKVS vector $p$, block-packed as ciphertexts of $\half$ slots, and
the other holds a batch of queries $\{y_j\}$ and wants output ciphertexts whose slots
contain $\langle\row(y_j),p\rangle$. Since decoding is linear, the batch is one plain
matrix--ciphertext vector product, where the plain matrix is determined by the
underlying OKVS rows; and since the decoder controls where each query's result lands,
the matrix can be organized \emph{diagonally}. For a generic matrix this diagonal
method costs one rotation per diagonal; the RSB spacing is what removes them. After
$\pi_\half$, the $\band$ nonzeros of every row sit one per consecutive block \emph{at
the same intra-block slot}, so each block contributes through a slot-aligned $\PMult$
and the contributions add without any slot movement: the whole product needs only
$\PMult/\CAdd$, up to the wrap bookkeeping at block boundaries which Section~\ref{sec:dense}
is about.

\paragraph{Sequencing.}
Distinct queries can be assigned the same output slot (their bands start in the same
block window at the same intra-block position). KKLS resolve these collisions by
\emph{sequencing}: greedily partition the $n_y$ queries into $L$ layers, assigning
query $j$ a pair $(\mu_j,\tau_j)$ --- layer and slot --- such that within each layer all
occupied slots are distinct and each layer's band starts span at most $\zeta$ blocks,
so a layer touches only $\sim\band+\zeta$ diagonals rather than all $b$. Each layer
becomes one output ciphertext. Two facts matter later:
\begin{enumerate}
  \item The assignment $(\mu_j,\tau_j)$ depends only on $H_1(F(y_j))$ (the band
  start of the key digest $F(y_j)$), the slot count, and $\zeta$. In particular the
  slot coordinate $\tau_j$ is a \emph{deterministic public function}
  $\tau(F(y_j))$ of the digest alone, while the layer $\mu_j$ additionally depends
  on which other queries collide.
  \item In the well-filled regime $\half\ll n_y$ a balls-into-bins argument gives
  $L\approx n_y/\half$ layers, i.e.\ the layout's \emph{fill rate}
  $n_y/(L\half)$ is close to $1$ and each slot column carries on average
  $\lambda:=n_y/\half\approx L$ queries.
\end{enumerate}

\subsection{The KKLS ssPMT}
\label{sec:prelim:sspmt}

The secret-shared private membership test is the two-party functionality of
Figure~\ref{fig:sspmt}: it tells the parties, in XOR-shared form, which of the
receiver's identifiers the sender also holds, while neither party learns the
membership bits themselves.

\begin{figure}[t]
\begin{funcbox}
\begin{center}
  \textbf{Functionality $\Fsspmt$}
\end{center}
\textbf{Parameters:} set sizes $n_x$, $n_y$.
\begin{itemize}
  \item[] \textbf{Inputs:} $\Snd$ inputs a set $X=\{x_i\}_{i\in[n_x]}$; $\Rcv$ inputs an
  ordered tuple $Y=(y_1,\dots,y_{n_y})$.
  \item[] \textbf{Output:} for each $j\in[n_y]$, sample bits
  $b_{\Snd,j},b_{\Rcv,j}\gets\{0,1\}$ uniformly subject to
  $b_{\Snd,j}\oplus b_{\Rcv,j}=\mathbf 1(y_j\in X)$. Give $(b_{\Snd,j})_{j\in[n_y]}$ to
  $\Snd$ and $(b_{\Rcv,j})_{j\in[n_y]}$ to $\Rcv$.
\end{itemize}
\end{funcbox}
\caption{The secret-shared private membership test functionality.}
\label{fig:sspmt}
\end{figure}

The KKLS instantiation (Appendix~D of~\cite{EPRINT:KwaKwoLeeSon26}) runs the batch
decode of Section~\ref{sec:prelim:homdec} on an \emph{indicator} OKVS: $\Snd$ encodes
$P\gets\Okvs.\mathsf{Encode}(\{(F(x_i),I_\Snd)\}_i)$ with a \emph{constant} target
string $I_\Snd$, and sends it encrypted; $\Rcv$ homomorphically decodes at its own
queries in its own sequenced layout, masks each occupied slot with a fresh random
$r_j$, and returns the result; $\Snd$ decrypts, obtaining
$d_j+r_j$ with $d_j=\langle\row(F(y_j)),P\rangle$ ($=I_\Snd$ on a match, garbage
otherwise); finally a secret-shared equality test between $\Snd$'s
$d_j+r_j-I_\Snd$ and $\Rcv$'s $r_j$ yields the XOR-shared membership bit.

\begin{remark}[born aligned]\label{rmk:bornaligned}
Because the decode is \emph{encrypted}, the constant target $I_\Snd$ is permissible:
$\Rcv$ never sees $d_j$ in the clear. (A plaintext OPPRF cannot use a constant
target --- the receiver would observe the repeated value on every match, leaking
membership directly.) The consequence is that the resulting shares are indexed by
$\Rcv$'s decode layout $(\mu_j,\tau_j)$ \emph{from birth}: no re-alignment step is
needed downstream. This property is what makes the layout itself a first-class
protocol object --- and what makes its disclosure (Section~\ref{sec:leak}) tempting.
\end{remark}

% ===========================================================================
\section{The Dense Two-Row BGV Decode}
\label{sec:dense}

\subsection{Slot Geometry: Why BGV Is Not Flat}
\label{sec:dense:geometry}

The spaced-band decode needs the $r$-slot cyclic shifts $\rr_r(c)$ of each block
ciphertext, for the $\sim\band{-}1$ wrap offsets at block boundaries. Two ways to get
them: \emph{(i)~pre-rotation} --- $\Snd$ sends the shifted copies in the clear and the
receiver does only $\PMult$s (more communication, no key switching); \emph{(ii)~homomorphic
rotation} --- the receiver builds $\rr_r$ itself from Galois keys, so $\Snd$ ships only
the base blocks plus the keys. In CKKS option~(ii) needs just a \emph{single} $1$-slot
key: its $N/2$ slots form one cyclic group $\Z_{N/2}$, so $\rr_r=\rr_1^{\,r}$ acts
cyclically on all of them. The BGV/BFV subtlety is that the $N$ slots do \emph{not}
form $\Z_N$: the slot group is $\Z_{N/2}\times\Z_2$ (an $N/2$-cyclic ``row'' direction
and an order-$2$ ``column'' swap), so a flat $N$-cyclic shift is \emph{not} an
automorphism and a single $1$-slot key is confined to one $N/2$ row. A naive $1$-key
approach therefore either uses only $N/2$ of the $N$ slots (one block per ciphertext:
this doubles $b$ and the layer depth, and is a strict loss --- $2.9$\,s / $95$\,MB at
the benchmark point of Section~\ref{sec:dense:eval}) or must handle the two rows
explicitly. This section shows the explicit handling costs almost nothing.

\subsection{The Construction}
\label{sec:dense:construction}

Write $\half:=N/2$. Pack \emph{two} $\half$-blocks per input ciphertext,
\[
  C_t=\Enc(p_{2t}\Vert p_{2t+1}),\qquad t<\lceil b/2\rceil,\quad b=m/\half,
\]
where $u\Vert v$ places $u$ in row $0$ and $v$ in row $1$. Each \emph{output}
ciphertext carries \emph{two} sequenced layers --- layer $2j$ in row $0$, layer
$2j{+}1$ in row $1$ --- so both rows hold a full inner product and the receiver returns
only $L/2$ ciphertexts. The obstruction is that a layer's width-$\band$ band spans
consecutive blocks of \emph{both} parities: even blocks sit in row $0$ of the paired
input, odd blocks in row $1$. To route an odd block into a row-$0$ (layer-$2j$) output
--- or an even block into a row-$1$ output --- one multiplies by the column-swapped
input $\colswap(C_t)=\Enc(p_{2t+1}\Vert p_{2t})$. Crucially $\colswap(C_t)$ is a
function of the \emph{input}: it is computed \emph{once per input ciphertext} and
reused across all output layers ($m/N$ swaps total), rather than a per-output
row-merge (which would cost one column rotation per layer, $L$ of them --- always the
wrong side to rotate, cf.\ Section~\ref{sec:dense:geometry}). Interleaving the two
layers' diagonals by row,
\[
  D^{\mathrm{dir}}=\big(\mathrm{diag}_{2j,2t}\,\Vert\,\mathrm{diag}_{2j+1,2t+1}\big),
  \qquad
  D^{\mathrm{swp}}=\big(\mathrm{diag}_{2j,2t+1}\,\Vert\,\mathrm{diag}_{2j+1,2t}\big),
\]
then lands every contribution in its correct output row
(Algorithm~\ref{alg:homdecode-bgv}), with row $0$ giving layer $2j$'s result and row
$1$ layer $2j{+}1$'s --- no merge. The wrap shifts $\rr_r$ act on both rows at once,
so a single shift serves both layers; only the $\sim\band{-}1$ wrapping blocks need
them, on both $C_t$ and $\colswap(C_t)$, giving $\sim\band{-}1$ row rotations. Total
receiver rotations: $m/N+(\band{-}1)$, under two Galois keys (row $+1$ and column
$\colswap$).

\begin{algorithm}[t]
\caption{$\HomDec_{\mathrm{BGV}}$ --- dense two-row decode (two layers per output ciphertext, input column-swap schedule)}
\label{alg:homdecode-bgv}
\begin{algorithmic}[1]
\Require paired ciphertexts $C_t=\Enc(p_{2t}\Vert p_{2t+1})$, $t<\lceil b/2\rceil$,
$\half=N/2$, $b=m/\half$; query keys $\{y_j\}$; Galois keys for row rotation $\rr_1$
and column swap $\colswap$
\State build the $\half$-spaced RSB matrix from $\{y_j\}$; sequence into layers
(span $\le\zeta$); form diagonals $\mathrm{diag}_{\ell,g,r}\in\Zp^{\half}$
(layer $\ell$, block $g$, wrap $r$); pair layers $2j\!\leftrightarrow\!2j{+}1$
\For{each referenced input pair $t$} \Comment{once; reused across all output ciphertexts}
  \State $R^0_{t,0}\gets C_t$;\quad $R^1_{t,0}\gets \colswap(C_t)$ \Comment{one column swap per input ciphertext}
  \For{$r=1$ to $\mathrm{maxwrap}(t)$} \Comment{only the $\sim\band{-}1$ wrapping blocks}
     \State $R^0_{t,r}\gets \rr_1(R^0_{t,r-1})$;\quad $R^1_{t,r}\gets \rr_1(R^1_{t,r-1})$ \Comment{$\rr_1$ shifts both rows/layers together}
  \EndFor
\EndFor
\For{each output ciphertext $j$} \Comment{layer $2j\to$ row $0$, layer $2j{+}1\to$ row $1$}
  \State $c^\ast_j \gets 0$
  \For{each referenced pair $t$ and wrap $r$}
     \State $c^\ast_j \gets c^\ast_j + \PMult\!\big(R^0_{t,r},\ \mathrm{diag}_{2j,\,2t,\,r}\Vert\mathrm{diag}_{2j{+}1,\,2t{+}1,\,r}\big)$ \Comment{even$\to$row $0$, odd$\to$row $1$}
     \State $c^\ast_j \gets c^\ast_j + \PMult\!\big(R^1_{t,r},\ \mathrm{diag}_{2j,\,2t{+}1,\,r}\Vert\mathrm{diag}_{2j{+}1,\,2t,\,r}\big)$ \Comment{odd$\to$row $0$, even$\to$row $1$}
  \EndFor
\EndFor
\State \Return $\{c^\ast_j\}$ \Comment{row $0$ of $c^\ast_j=\langle\row(y),p\rangle$ for layer $2j$; row $1$ for layer $2j{+}1$}
\end{algorithmic}
\end{algorithm}

\begin{proposition}[correctness, row-wise]\label{prop:dense-correct}
For every query $y$ assigned $(\mu,\tau)$ by the sequencing, slot $\tau$ of row
$(\mu\bmod 2)$ of output ciphertext $\lfloor\mu/2\rfloor$ of
Algorithm~\ref{alg:homdecode-bgv} decrypts to $\langle\row(y),p\rangle$. In
particular each query's inner product is assembled entirely within one row --- no
contribution ever needs to cross rows after the input swap --- so no per-output merge
is required.
\end{proposition}

\begin{proof}
\TODO{Write out. Sketch: fix layer $2j$ (row $0$; row $1$ is symmetric). Its band
coordinate in block $g$ contributes $\mathrm{diag}_{2j,g,r}[\tau]\cdot p_g[\tau-r]$
for the appropriate wrap $r$. If $g=2t$ is even, $p_g$ sits in row $0$ of $C_t$, and
the term is produced by the $R^0_{t,r}$ multiply (whose row-$0$ diagonal is
$\mathrm{diag}_{2j,2t,r}$). If $g=2t{+}1$ is odd, $p_g$ sits in row $1$ of $C_t$,
hence in row $0$ of $\colswap(C_t)=R^1_{t,0}$, and the term is produced by the
$R^1_{t,r}$ multiply (row-$0$ diagonal $\mathrm{diag}_{2j,2t+1,r}$). Since $\rr_1$
rotates the two rows in parallel and $\PMult$ is slot-wise, row $0$ of the
accumulator only ever receives layer-$2j$ terms, and every in-band block of layer
$2j$ is covered exactly once. Also handle: wrap at the pairing boundary
$t=\lceil b/2\rceil-1$ (odd $b$), and queries whose band wraps modulo $m$.}
\end{proof}

\subsection{Rotation Schedules and Optimality}
\label{sec:dense:schedules}

\paragraph{Output-swap schedule (the default).}
The swap can instead be folded through the automorphism identity
\begin{equation}\label{eq:swapfold}
  D\odot\colswap(x)=\colswap\big(\colswap(D)\odot x\big),
\end{equation}
where $\odot$ is the slot-wise plaintext multiply: since $\colswap(D^{\mathrm{swp}})$
is a \emph{free} plaintext-side row swap, every $\PMult$ runs against $\rr_r(C_t)$
only --- $\colswap(C_t)$ is never formed, halving the wrap shifts to
$\lceil(\band{-}1)/2\rceil$ --- the swapped-orientation terms accumulate separately,
and the accumulator is column-swapped \emph{once per output ciphertext}:
\[
  c^\ast_j=\mathrm{acc}^{\mathrm{dir}}_j+\colswap\big(\mathrm{acc}^{\mathrm{swp}}_j\big).
\]
Total $L/2+(\band{-}1)/2$ rotations, which beats the input-swap count
$m/N+(\band{-}1)$ whenever $L/2<m/N+(\band{-}1)/2$ --- in our whole operating range
(e.g.\ $n=2^{20}$, $\eps=1.1$: $207$ vs.\ $299$ rotations) --- and gains $\approx1$
bit of noise budget because the key switch lands \emph{after} the plain-multiply sum.
The implementation provides both schedules; the output-swap one is the default.

\TODO{State the output-swap variant as a displayed algorithm or as a diff against
Algorithm~\ref{alg:homdecode-bgv} (replace lines 3--5 by $R_{t,r}=\rr_1^r(C_t)$ only;
keep two accumulators per output, apply~\eqref{eq:swapfold} to the swapped diagonals;
one $\colswap$ per output at the end).}

\paragraph{The schedule space.}
\TODO{Systematize the four layouts and prove the dominance claims:
\begin{itemize}
  \item \emph{Input column-swap}: $m/N+(\band{-}1)$ rotations
  (Algorithm~\ref{alg:homdecode-bgv}).
  \item \emph{Output column-swap}: $L/2+(\band{-}1)/2$ rotations; dominates
  input-swap iff $L/2<m/N+(\band{-}1)/2$, which holds throughout the deployment
  range since $L\approx n_y/\half$ grows slowly while $m/N$ grows linearly in
  $\eps$. Additionally $\approx1$ bit better in noise (key switch after the sum).
  \item \emph{Replicated $p$} (column-swap-free): ship both orientations of every
  block, $2\times$ input communication; dominated.
  \item \emph{Per-output merge} (one query split across the rows): $(\band{-}1)/2+L$
  rotations; dominated by output-swap ($L$ vs.\ $L/2$ on the dominant term).
\end{itemize}
Give the noise-budget accounting for input- vs.\ output-swap (where each key switch
sits relative to the $\PMult$ sums), and the two-Galois-key material cost
($1.4$\,MB at the benchmark parameters).}

\subsection{Integrated Sequencing (Open)}
\label{sec:dense:intseq}

The current implementation sequences at $\half=N/2$ slots and pairs layers afterwards
(\emph{sequence-then-pair}). This is wasteful in $\PMult$s: the two layers of a pair
have independent block windows, so the pair's union window --- what the output
ciphertext actually pays for --- is up to twice $\zeta$. An \emph{integrated}
sequencing that fills both rows of each paired layer under one shared block window
$\le\zeta$ would cut the plain-multiply count to a projected $0.97$--$1.04\times$ the
$N$-slot decode, versus the measured $1.18$--$1.41\times$ of sequence-then-pair.

\TODO{(1)~Design: extend the greedy sequencer to assign $(\mu_j,\tau_j)$ with
$\mu_j$ ranging over \emph{paired} layers and a single span constraint per pair;
queries of both parities compete for the same window. Check the balls-into-bins
analysis still gives $L\approx n_y/\half$ (now $L/2$ pairs). (2)~Implement in the
existing BGV decode (this repository: \texttt{experiments/}, \texttt{rlwe-okvs/},
\texttt{exec/}).
(3)~Re-measure the sweep of Appendix~\ref{app:epssweep}; the projection
$0.97$--$1.04\times$ is measurement-based extrapolation, not yet a measurement.}

\subsection{Measured Performance}
\label{sec:dense:eval}

At $n=2^{20}$ queries with ring dimension $N=2^{13}$, the receiver-side decode
(diagonal-plaintext encoding included in the timing) matches or beats the base RPMT
reference of $2.0$\,s / $58$\,MB: $1.8$\,s / $53$\,MB pre-rotated, $1.8$\,s /
$49$\,MB dense two-row with the output-swap schedule. Correctness is verified exactly
over $\Zp$ for all queries. The full redundancy sweep (Appendix~\ref{app:epssweep})
shows the structural difference between the layouts: pre-rotated communication is
\emph{U-shaped} in $\eps$ (the $\band{-}1$ shifted copies grow as $\eps$ shrinks),
bottoming out near $\eps\approx0.4$ at $43$\,MB, while dense communication
$\approx(1+\eps)\tfrac nN$ ciphertexts is \emph{monotone} --- so only the dense
layout can exploit the small-$\eps$ regime ($28.5$\,MB at $\eps=0.2$, $-38\%$). In
time, output-swap crosses pre-rotation near $\eps\approx0.6$--$0.7$: below, dense is
faster as well; above, pre-rotation stays ahead by $2$--$5\%$.

\TODO{Machine spec, library/version, thread count; re-run after integrated
sequencing lands; add the $L/2$ return-ciphertext saving to the communication
accounting (currently reported one-directional).}

% ===========================================================================
\section{Leakage of Layout Disclosure in the Standalone ssPMT}
\label{sec:leak}

\subsection{The Optimization, and Why It Is Tempting}
\label{sec:leak:setting}

In the KKLS ssPMT (Section~\ref{sec:prelim:sspmt}), the equality phase runs one
secret-shared equality instance per decode position. $\Rcv$'s occupied positions are
the $n_y$ pairs $(\mu_j,\tau_j)$, but $\Snd$ does not know which of the $L\half$
positions those are --- the layout depends on $Y$ --- so the baseline protocol runs
the equality test at \emph{every} position of the deterministic full layout, with
$\Rcv$ supplying dummies at the $L\half-n_y$ unoccupied ones. A natural optimization
is therefore:
\begin{quote}
  \emph{$\Rcv$ discloses its occupancy set
  $\occ(Y)=\{(\mu_j,\tau_j):j\in[n_y]\}$ (equivalently, an $L\times\half$ bitset)
  to $\Snd$, and the parties run only $n_y$ equality instances.}
\end{quote}
Since the fill rate $n_y/(L\half)$ is $0.7$--$0.9$ in well-filled deployments, the
saving looks like a harmless constant factor. This section shows the disclosure is
\emph{not} harmless, quantifies exactly what it leaks, and repairs it.

The attack surface is specific to the \emph{standalone} ssPMT, where $\Snd$ encodes
the indicator OKVS at the digests $F(x_i)$ of its own items and therefore
\emph{knows} $F(x)$ for every candidate $x\in X$: by
Section~\ref{sec:prelim:homdec}, the slot column
$\tau(F(x))$ --- determined by the band start $H_1(F(x))$, the slot count, and
$\zeta$ --- is a public deterministic function that $\Snd$ can evaluate
itself.\footnote{Contrast the Real-PJC alignment protocol, which discloses a related
correspondence safely: there the digests are $\mathrm{OPRF}$ values under
\emph{$\Rcv$'s} key, so the sender cannot evaluate any candidate's coordinates, and
the occupancy pattern is simulatable from $n_y$ alone. The analysis below makes
precise that this OPRF direction is load-bearing: the moment the sender can predict
coordinates, occupancy disclosure leaks.}

\subsection{The Leakage Observable}
\label{sec:leak:observable}

Under the disclosure, $\Snd$'s view includes $\occ(Y)$. For a candidate $x$, the
relevant statistic is the \emph{column multiplicity}
\[
  m_\tau \;=\; \big|\{\,j\in[n_y] \;:\; \tau(F(y_j))=\tau\,\}\big|
  \;=\; \big|\{\,\mu \;:\; (\mu,\tau)\in\occ(Y)\,\}\big|,
  \qquad \tau=\tau(F(x)),
\]
i.e.\ the number of layers in which $\Snd$'s predicted column for $x$ is occupied.
(The layer coordinates $\mu_j$ carry no additional per-candidate information in the
idealized model below: $\Snd$ can predict $\tau(F(x))$ but not $\mu$, which depends
on the unknown collision pattern of all of $Y$.)

\paragraph{Model.}
We analyze the idealized assignment in which each $y_j$ is routed to an independent
uniform column, $\tau(F(y_j))\sim U[\half]$ --- the standard random-oracle model for
$H_1\circ F$, exact up to the sequencer's tie-breaking. Write
\[
  \lambda:=\frac{n_y}{\half}
\]
for the mean column load; in the well-filled regime $\lambda\approx L$
(Section~\ref{sec:prelim:homdec}). Then, for a fixed candidate $x$ with
$\tau=\tau(F(x))$:
\begin{align*}
  \text{if } x\notin Y:&\quad m_\tau \sim \Bin(n_y,\,1/\half)\;\approx\;\Poi(\lambda),\\
  \text{if } x\in Y:&\quad m_\tau \sim 1+\Bin(n_y-1,\,1/\half)\;\approx\;1+\Poi(\lambda),
\end{align*}
the member's own query contributing the deterministic $+1$. We state the results for
the Poisson limit; the binomial corrections are $O(1/n_y)$ and do not affect any
conclusion. \TODO{Make the approximation claim precise (Le~Cam / monotonicity of the
tests below under the exact binomial pair).}

\subsection{Optimal Distinguishing: the Likelihood-Ratio Test}
\label{sec:leak:lr}

\begin{proposition}[the LR test, and its optimality]\label{prop:lr}
Let $P_0=\Poi(\lambda)$ (non-member) and $P_1=1+\Poi(\lambda)$ (member). The
likelihood ratio at an observed multiplicity $m\ge0$ is
\[
  \LR(m)\;=\;\frac{P_1(m)}{P_0(m)}\;=\;\frac{e^{-\lambda}\lambda^{m-1}/(m-1)!}
  {e^{-\lambda}\lambda^{m}/m!}\;=\;\frac{m}{\lambda}
  \qquad(\text{with }\LR(0)=0),
\]
which is nondecreasing in $m$. Consequently, by the Neyman--Pearson lemma, every
optimal test is a threshold test on $m$; with equal priors the Bayes-optimal decision
is
\[
  \text{declare ``member''}\iff m\ge\lambda
  \quad(\text{i.e.\ }m\ge\lceil\lambda\rceil\text{ for non-integer }\lambda),
\]
and its distinguishing advantage equals $\TV(P_0,P_1)$.
\end{proposition}

\begin{proof}
The likelihood ratio is immediate from $P_1(m)=P_0(m-1)$. Monotonicity gives the
threshold form via Neyman--Pearson; the Bayes rule accepts exactly when $\LR(m)\ge1$,
i.e.\ $m\ge\lambda$. The advantage of the Bayes rule under equal priors is
$\tfrac12+\tfrac12\TV(P_0,P_1)$ minus $\tfrac12$, i.e.\ $\TV(P_0,P_1)$ up to the
factor-$\tfrac12$ convention. \TODO{Fix one advantage convention and use it
throughout; currently ``advantage'' $=\TV$ and ``success probability''
$=\tfrac12+\tfrac12\TV$.}
\end{proof}

The value of $\TV(P_0,P_1)$ has a clean closed form, as an instance of a general fact
about unit shifts of unimodal lattice distributions.

\begin{lemma}[$\TV$ of a unit shift $=$ mode mass]\label{lem:tvmode}
Let $P$ be a probability distribution on $\Z$ that is unimodal with mode $m^\ast$:
$P(m)\ge P(m-1)$ for $m\le m^\ast$ and $P(m)\le P(m-1)$ for $m>m^\ast$. Let $Q$ be
its unit shift, $Q(m)=P(m-1)$. Then
\[
  \TV(P,Q)\;=\;P(m^\ast).
\]
\end{lemma}

\begin{proof}
By definition $2\,\TV(P,Q)=\sum_{m\in\Z}\lvert P(m)-P(m-1)\rvert$. Unimodality fixes
the signs: the differences are nonnegative for $m\le m^\ast$ and nonpositive for
$m>m^\ast$, so the sum telescopes,
\[
  \sum_{m\le m^\ast}\big(P(m)-P(m-1)\big)
  +\sum_{m>m^\ast}\big(P(m-1)-P(m)\big)
  \;=\;P(m^\ast)+P(m^\ast),
\]
whence $\TV(P,Q)=P(m^\ast)$.
\end{proof}

\begin{corollary}[per-candidate advantage]\label{cor:advantage}
$\Poi(\lambda)$ is unimodal with mode $\lfloor\lambda\rfloor$, so
\[
  \TV\big(\Poi(\lambda),\,1+\Poi(\lambda)\big)
  \;=\;\Pr\big[\Poi(\lambda)=\lfloor\lambda\rfloor\big]
  \;=\;e^{-\lambda}\frac{\lambda^{\lfloor\lambda\rfloor}}{\lfloor\lambda\rfloor!}
  \;\approx\;\frac{1}{\sqrt{2\pi\lambda}},
\]
by Stirling. The per-candidate leakage therefore decays only as
$\lambda^{-1/2}$: at $\lambda=128$ (e.g.\ $n_y=2^{20}$, $\half=2^{13}$) the advantage
is $\approx3.5\%$ and the optimal test's success probability is
$\approx\tfrac12+1.8\%$ per candidate --- far from negligible in the cryptographic
sense, for \emph{every} parameter regime.
\end{corollary}

\subsection{The Empty-Column Certificate}
\label{sec:leak:certificate}

The average-case advantage of Corollary~\ref{cor:advantage} understates the
qualitative danger. Since $\LR(0)=0$, the event $m_{\tau(F(x))}=0$ is not merely
evidence --- it is a \emph{certificate}: a member's own query always contributes, so
an empty column proves $x\notin Y$ with no error. The certificate fires on a
non-member with probability
\[
  \Pr\big[\Poi(\lambda)=0\big]=e^{-\lambda}.
\]
Two regimes:
\begin{itemize}
  \item \emph{Well-filled layouts} ($\lambda\approx128$): $e^{-\lambda}$ is
  astronomically small; the leakage is the ``soft'' $\lambda^{-1/2}$ advantage only.
  \item \emph{Sparse layouts} ($\lambda\approx1$, i.e.\ $n_y\lesssim\half$): a
  fraction $e^{-1}\approx37\%$ of all non-member candidates receive a definite
  exclusion certificate. $\Snd$ can scan any candidate list and \emph{certifiably}
  rule out a third of the non-members --- a qualitatively different leakage class.
\end{itemize}
The leakage is thus governed by the batching parameters: the same disclosure is a
few-percent distinguisher in one deployment and a bulk membership filter in another.
Any leakage-explicit variant (Section~\ref{sec:leak:repair}) must carry a lower bound
on $\lambda$ as a security parameter, not a performance knob.

\subsection{Aggregate Statistics Are Not New Leakage}
\label{sec:leak:aggregate}

$\Snd$ can also aggregate: $\sum_{x\in X}m_{\tau(F(x))}$ concentrates around
$|X\cap Y|+n_x\lambda$, yielding an estimator of the intersection cardinality. In the
applications consuming ssPMT, the intersection cardinality is part of the intended
output (or is revealed by the downstream functionality), so we do not count this as
new leakage; the per-candidate tests above are the genuine damage. \TODO{Say this
carefully: if ssPMT is used inside a functionality that hides the cardinality, the
aggregate estimator \emph{is} new leakage and the repair of
Section~\ref{sec:leak:repair} is mandatory regardless of $\lambda$.}

\subsection{Amplification: the Consistency Oracle}
\label{sec:leak:oracle}

\VERIFY{This subsection is a session-derived analysis and has not yet been
independently re-derived; re-check the error probability and the dummy-padding claim
before publication.}

The disclosure becomes fatal when the layout is published \emph{jointly} with a
second coordinate system that $\Snd$ can also predict. The canonical example is a
correspondence table
\[
  \sigma:\ \mathrm{bin}\longmapsto(\mu,\tau)
\]
between a circuit-PSI-style cuckoo layout (bins of $F(y_j)$) and the decode layout
--- exactly the object one would publish to splice the ssPMT shares into an existing
cuckoo-indexed protocol. Now $\Snd$ holds, for every candidate $x$, \emph{two}
predictable coordinates: the cuckoo bin $\mathrm{bin}(F(x))$ and the slot column
$\tau(F(x))$. It checks their \emph{consistency}: does $\sigma$ map (one of) $x$'s
candidate bins to a position in column $\tau(F(x))$?
\begin{itemize}
  \item If $x\in Y$, the pair is consistent by construction --- always.
  \item If $x\notin Y$, consistency requires some other $y_j$ to occupy one of
  $x$'s bins \emph{and} agree with $x$'s column, which happens with probability
  $\approx1/\half$ per bin.
\end{itemize}
The consistency check is therefore a per-item membership test with one-sided error
$O(1/\half)$ --- essentially perfect at any realistic $\half$. Note the contrast with
Section~\ref{sec:leak:lr}: pairing two coordinates converts a
$\lambda^{-1/2}$-advantage statistical test into an exact oracle. Dummy padding does
\emph{not} help: padding adds spurious occupied positions, but every \emph{real}
item's pair remains consistent, so the one-sided test survives (the padding only
perturbs the already-negligible false-positive rate \VERIFY{check the direction of
this perturbation}).

\begin{center}
\emph{Design rule: never publish the pairing of two coordinate systems that the
sender can evaluate on candidate inputs.}
\end{center}

\subsection{Repairs}
\label{sec:leak:repair}

\paragraph{Repair 1: do not disclose (the default).}
Run the equality phase over the \emph{full deterministic layout}: all $L\half$
positions, with $\Rcv$ supplying uniformly random dummy shares at unoccupied
positions (equivalently: $\Rcv$ pads its input with dummy queries until every slot
is occupied). The cost is a factor $1/\text{fill-rate}\approx1.1$--$1.4$ in the
equality phase --- constant, and small precisely in the well-filled regime where one
would deploy. Security becomes trivial: $\Snd$'s view no longer contains
\emph{any} $Y$-dependent object --- the layout dimensions $(L,\half)$ are public
functions of $n_y$ alone --- so the simulator is immediate.
\TODO{State and prove the simulation lemma; fold into the ssPMT security proof of
the base paper. Also specify the deterministic rule for $L$ (e.g.\
$L=\lceil(1+\delta)n_y/\half\rceil$ with public $\delta$) so that $L$ itself does
not leak the sequencer's collision pattern; bound the failure probability that the
sequencer needs more than $L$ layers.}

\paragraph{Repair 2: leakage-explicit compression.}
If the $n_y$-instance variant is truly needed, it must be stated as security with
leakage: the ideal functionality additionally hands $\Snd$ the leakage
\[
  \mathcal{L}(Y)\;=\;\occ(Y)
  \quad\big(\text{equivalently, up to simulation, the column-multiplicity profile }
  (m_\tau)_{\tau\in[\half]}\big),
\]
together with the quantitative consequences of
Sections~\ref{sec:leak:lr}--\ref{sec:leak:certificate}: per-candidate advantage
$\approx1/\sqrt{2\pi\lambda}$ and exclusion-certificate rate $e^{-\lambda}$. A
deployment bound $\lambda\ge\lambda_{\min}$ must be part of the parameter
specification (ruling out sparse layouts), and composition with any second
predictable coordinate system (Section~\ref{sec:leak:oracle}) must be forbidden
explicitly. \TODO{Formalize as a leakage function in the simulation statement;
decide whether to also charge the aggregate cardinality estimator
(Section~\ref{sec:leak:aggregate}) depending on the enclosing functionality.}

\paragraph{Non-repair: coordinate hiding.}
Partial mitigations that randomize coordinates --- e.g.\ a secret per-layer rotation
of the slot columns before disclosure --- do \emph{not} yield a clean claim: the
disclosed pattern retains rotation-invariant structure (the multiset of gaps between
occupied columns within a layer, cross-layer column correlations), so a
pair-correlation variant of the test of Section~\ref{sec:leak:lr} survives. We do
not recommend pursuing this direction. \VERIFY{Session-derived; if this route is
ever needed, the pair-correlation attack should be worked out or refuted properly.}

\subsection{Cost of the Repair}
\label{sec:leak:cost}
\TODO{Measure the ss-equality phase at $n_y$ vs.\ $L\half$ instances across the
sweep parameters (fill rates $0.7$--$0.9$): communication and time, for the
circuit-PSI-based instantiation~\cite{EC:PSTY19,AC:LPRST21}. Expected verdict: the
full-layout repair costs $1.1$--$1.4\times$ in the equality phase only, which is a
small fraction of end-to-end cost --- i.e.\ the safe default is cheap.}

% ===========================================================================
\section*{Acknowledgements}
\TODO{grants.}

% ===========================================================================
% Bibliography
% ===========================================================================
\bibliographystyle{splncs04}
\bibliography{abbrev2,crypto_crossref,mybib}

% ===========================================================================
\appendix

\section{Redundancy Sweep for the BGV Indicator Decode}
\label{app:epssweep}

Table~\ref{tab:epssweep} reports the full redundancy sweep behind the discussion of
Section~\ref{sec:dense:eval}, at $n=2^{20}$ with ring degree $N=2^{13}$ (BGV, coefficient
modulus $\{60,50,50,60\}$, $\log p=40$). For each expansion $m/n=1+\eps$ the band width $\band$
is the smallest width whose extrapolated encoding-failure rate is below $2^{-40}$ (probe-fit),
and the sequencing span is $\zeta=\max(8,\lfloor0.65\band\rceil)$. Time is the full wall clock of
one decode instance --- band generation and OKVS encoding, encryption of the transmitted
ciphertexts, and the receiver-side decode (diagonal-plaintext encoding included) --- single-threaded%
\TODO{machine spec}. Communication is the sender-to-receiver transmission with seeded (symmetric)
serialization ($\approx0.18$\,MB per ciphertext); the dense layout additionally ships its two
Galois keys ($1.4$\,MB, included) and, in the reverse direction, returns only $L/2$ output
ciphertexts (half of the pre-rotated variant's $L$; not included in the table).

The dense layout is measured in both rotation schedules: \emph{input column-swap} ($\colswap$ on
each input ciphertext, reused across layers: $m/N+(\band{-}1)$ rotations) and \emph{output swap}
(the swapped-orientation terms are folded through $D\odot\colswap(x)=\colswap(\colswap(D)\odot x)$,
with $\colswap(D)$ a free plaintext row swap, and column-swapped once per \emph{output}:
$L/2+(\band{-}1)/2$ rotations). Two features are visible. First, the pre-rotated communication is
\emph{U-shaped} in $\eps$ (the $\band-1$ shifted copies grow as $\eps$ shrinks), bottoming out
near $\eps\approx0.4$ at $43$\,MB, while the dense communication $\approx(1+\eps)\tfrac nN$
ciphertexts is monotone --- so only the dense layout can exploit the small-$\eps$ regime
($28.5$\,MB at $\eps=0.2$, $-38\%$). Second, the output-swap schedule dominates the input-swap
one throughout (fewer rotations, and the key switch lands \emph{after} the plain-multiply sum,
gaining $\approx1$ bit of noise budget); against pre-rotation its total time crosses near
$\eps\approx0.6$--$0.7$ --- below, the dense layout is the faster one as well (the shared
OKVS-encoding cost $O(n\band^2)$ dominates), above, pre-rotation stays ahead by $2$--$5\%$.

\begin{table}[h]
\centering
\caption{Redundancy sweep of the BGV indicator decode at $n=2^{20}$, $N=2^{13}$. ``ctxts'' counts
the ciphertexts the sender transmits (the dense layout adds two Galois keys, $1.4$\,MB,
included in its comm); ``rot'' counts the receiver's Galois rotations --- $m/N+(\band{-}1)$ for the
input-swap schedule, $L/2+(\band{-}1)/2$ for the output-swap one; time is the full wall clock
(encode $+$ encrypt $+$ decode).}
\label{tab:epssweep}
\setlength{\tabcolsep}{3.4pt}
\begin{tabular}{@{}ccc@{\hspace{11pt}}ccc@{\hspace{11pt}}cc@{\hspace{11pt}}cc@{\hspace{11pt}}cc@{}}
\toprule
&&& \multicolumn{3}{c@{\hspace{11pt}}}{Pre-rotated} & \multicolumn{2}{c@{\hspace{11pt}}}{Dense two-row} & \multicolumn{2}{c@{\hspace{11pt}}}{~~input swap} & \multicolumn{2}{c}{~~output swap}\\
\cmidrule(r{11pt}){4-6}\cmidrule(r{11pt}){7-8}\cmidrule(r{11pt}){9-10}\cmidrule{11-12}
$\eps$ & $\band$ & $\zeta$ & ctxts & comm & time & ctxts & comm & rot & time & rot & time\\
&&&& (MB) & (s) && (MB) & & (s) & & (s)\\
\midrule
0.2 & 110 & 72 & 263 & 46.3 & 7.11 & 154 & 28.5 & 264 & 6.91 & 212 & 6.40\\
0.3 &  81 & 53 & 247 & 43.5 & 5.02 & 167 & 30.8 & 247 & 4.90 & 200 & 4.84\\
0.4 &  67 & 44 & 246 & 43.3 & 4.11 & 180 & 33.1 & 246 & 4.08 & 190 & 4.05\\
0.5 &  58 & 38 & 249 & 43.8 & 3.62 & 192 & 35.2 & 250 & 3.66 & 191 & 3.58\\
0.6 &  50 & 33 & 254 & 44.7 & 3.27 & 205 & 37.5 & 255 & 3.32 & 193 & 3.25\\
0.7 &  43 & 28 & 260 & 45.8 & 2.89 & 218 & 39.8 & 260 & 2.97 & 191 & 2.90\\
0.8 &  42 & 27 & 272 & 47.9 & 2.83 & 231 & 42.1 & 273 & 2.95 & 194 & 2.86\\
0.9 &  38 & 25 & 281 & 49.5 & 2.66 & 244 & 44.4 & 282 & 2.77 & 193 & 2.67\\
1.0 &  34 & 22 & 289 & 50.9 & 2.46 & 256 & 46.5 & 290 & 2.61 & 201 & 2.52\\
1.1 &  31 & 20 & 299 & 52.6 & 2.34 & 269 & 48.8 & 299 & 2.48 & 207 & 2.42\\
1.2 &  30 & 20 & 311 & 54.7 & 2.33 & 282 & 51.1 & 312 & 2.49 & 210 & 2.41\\
1.3 &  30 & 20 & 324 & 57.0 & 2.35 & 295 & 53.3 & 325 & 2.50 & 209 & 2.41\\
1.4 &  28 & 18 & 335 & 59.0 & 2.25 & 308 & 55.6 & 336 & 2.44 & 218 & 2.36\\
1.5 &  27 & 18 & 346 & 60.9 & 2.24 & 320 & 57.7 & 346 & 2.42 & 218 & 2.32\\
1.7 &  25 & 16 & 370 & 65.1 & 2.17 & 346 & 62.3 & 370 & 2.33 & 227 & 2.23\\
2.0 &  23 & 15 & 406 & 71.5 & 2.12 & 384 & 69.0 & 406 & 2.32 & 242 & 2.22\\
\bottomrule
\end{tabular}
\end{table}

\end{document}
